\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-29 paper.qmd
small pieces in background

The solution is to use the tour to examine how the NLDR is warping the space.

@@

### pbmc
     - NLDR view used to illustrate clusters
     - Use our method to assess is it a reasonable representation
     - Demonstrate that it is not
     - Illustrate how to use out method to get a better representation

### digits: 1
     - NLDR is used to illustrate different ways 1's are drawn
     - Use our method to assess is it a reasonable representation
     - Demonstrate that it is, except for the anomalies

>>>>

The solution is to use the tour to examine how the NLDR is warping the space. This approach follows what @article08 describes as *model-in-the-data-space*. The fitted model should be overlaid on the

Linked brushing as done by @article21

@@

### pbmc

- NLDR view used to illustrate clusters
- Use our method to assess is it a reasonable representation
- Demonstrate that it is not
- Illustrate how to use out method to get a better representation

### digits: 1

- NLDR is used to illustrate different ways 1's are drawn
- Use our method to assess is it a reasonable representation
- Demonstrate that it is, except for the anomalies

### 2024-03-29 paper.tex
small pieces in background

The solution is to use the tour to examine how the NLDR is warping the
space.

@@

\begin{verbatim}
 - NLDR view used to illustrate clusters
 - Use our method to assess is it a reasonable representation
 - Demonstrate that it is not
 - Illustrate how to use out method to get a better representation

\end{verbatim}

@@

\begin{verbatim}
 - NLDR is used to illustrate different ways 1's are drawn
 - Use our method to assess is it a reasonable representation
 - Demonstrate that it is, except for the anomalies

\end{verbatim}

>>>>

The solution is to use the tour to examine how the NLDR is warping the
space. This approach follows what \citet{article08} describes as
\emph{model-in-the-data-space}.

@@

\begin{itemize}
\tightlist
\item
  NLDR view used to illustrate clusters
\item
  Use our method to assess is it a reasonable representation
\item
  Demonstrate that it is not
\item
  Illustrate how to use out method to get a better representation
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  NLDR is used to illustrate different ways 1's are drawn
\item
  Use our method to assess is it a reasonable representation
\item
  Demonstrate that it is, except for the anomalies
\end{itemize}
